% Professional Resume LaTeX Template
\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tikz}
\pagestyle{empty}

% Custom colors
\definecolor{primary}{HTML}{2575FC}
\definecolor{secondary}{HTML}{6A11CB}
\definecolor{sectionbg}{HTML}{F0F4FF}

% Section formatting
\newcommand{\sectionline}{\noindent\color{primary}\rule{\linewidth}{1pt}}

\begin{document}

% Background color
\begin{tikzpicture}[remember picture,overlay]
  \fill[sectionbg] (current page.south west) rectangle (current page.north east);
\end{tikzpicture}

% Header
\begin{center}
    {\LARGE \textbf{Your Name}} \\[2pt]
    \textcolor{secondary}{Software Engineer $\vert$ Full Stack Developer $\vert$ Web Designer} \\[2pt]
    \href{mailto:imkrisk@icloud.com}{imKrisK@icloud.com} $\vert$ 
    \href{https://linkedin.com/in/KristofferKelly}{linkedin.com/in/KristofferKelly} $\vert$ 
    \href{https://github.com/imKrisK}{github.com/imKrisK}
\end{center}

\vspace{0.5em}
\sectionline

% Professional Summary
\section*{Professional Summary}
Results-driven developer with experience in building scalable web applications and designing user-centric interfaces.

% Skills
\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item JavaScript, TypeScript, 
    \item React, Node.js, Express, MongoDB, SQL
    \item HTML5, CSS3, Figma, Bravo Studio, Tailwind CSS
    \item REST APIs, GraphQL, AWS, Docker
\end{itemize}

% Experience
\section*{Experience}
\textbf{Software Engineer, Company Name} \hfill Jan 2023 -- Present\\
\begin{itemize}[leftmargin=*]
    \item Developed scalable backend services using Node.js and Express.
    \item Collaborated with designers to create responsive web interfaces.
\end{itemize}

\textbf{Full Stack Developer, Another Company} \hfill Jun 2021 -- Dec 2022\\
\begin{itemize}[leftmargin=*]
    \item Built full stack applications with React and MongoDB.
    \item Implemented RESTful APIs and integrated third-party services.
\end{itemize}

% Projects
\section*{Projects}
\textbf{Portfolio Website}
\begin{itemize}[leftmargin=*]
    \item Designed and developed a personal portfolio using React and Figma.
\end{itemize}
\textbf{Open Source Contributor}
\begin{itemize}[leftmargin=*]
    \item Contributed to open source projects on GitHub, focusing on UI/UX improvements.
\end{itemize}

% Education
\section*{Education}
B.Sc. in Computer Science, University Name, 2021

\end{document}
